Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2020-04-07 article.tex
Add figure 1
Fix layout
EOD
Fine abstract

%comments
\newcommand{\frans}[1]{\textcolor{blue}{\textbf{[FB: #1]}}}
\newcommand{\richel}[1]{\textcolor{orange}{\textbf{[RB: #1]}}}
\newcommand{\rampal}[1]{\textcolor{green}{\textbf{[RSE: #1]}}}

@@

Transmembrane helices (TMHs) are an overrepresented source of epitopes on major 
histocompatibility complex (MHC) class I due to a preference for hydrophobic 
for the majority of HLA-I haplotypes. It is unknown why there is such a 
preference and whether  this is the case for MHC-II haplotypes. This study 
investigates if there is an evolutionary conservation of a pathogen’s TMHs 
and if this correlates with the affinity for binding to MHC-II.

TMHs more/less/equal as expected by chance. We ﬁnd that ...

@@

@@

@@

Thanks to Geert van den Bogaart for his help \richel{reword}.
Thanks to Maxim for his help \richel{reword}.
We thank the Netherlands 
Organization for Scientific Research (NWO) for financial support 
through a VICI grant awarded to RSE.

@@

RJCB and FB conceived the idea for this research. 
RJCB wrote the code.
FB supplied the DNA alignment.
RJCB, FB and RSE contributed to writing the article.

>>>>

%comments
\newcommand{\frans}[1]{\textcolor{blue}{\textbf{[FB: #1]}}}
\newcommand{\richel}[1]{\textcolor{orange}{\textbf{[RB: #1]}}}

@@

Transmembrane helices (TMHs) are an overrepresented source of epitopes on major 
histocompatibility complex (MHC) class I for the majority of HLA-I haplotypes. 
It is unknown why there is such a preference exists and 
whether this is the case for MHC-II haplotypes. 
This study shows that also MHC-II binds to polypeptides derived from TMHs 
more often than expected by chance. It is unknown if a signal of
natural selection is present in the proteome coding for TMHs.
This study shows that in the mutation rate in TMHs of [a pathogen] 
are [less/equal/more], hinting at 
evolutionary [conservation/neutrality/disruptive selection].
Our findings suggest that developing vaccines targeting the TMHs of
pathogens is a [good/neutral/bad] idea.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Hypotheses}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}
  \item $\mathcal{H}_1$: MHC-II binds as often to TMHs as the cytosolic and extracellular
    parts of a pathogen's transmembrane proteins
  \item $\mathcal{H}_2$: The TMHs of [a pathogen] have the same mutation rate 
    as the cytosolic and extracellular
    parts of its transmembrane proteins
\end{itemize}

@@

\begin{figure}[ht]
  \includegraphics[width=\textwidth]{figure_1.png}
  \label{fig:1}
\end{figure}

\begin{figure}[ht]
  \includegraphics[width=\textwidth]{figure_1_5.png}
  \label{fig:1_5}
\end{figure}

\begin{figure}[ht]
  \includegraphics[width=\textwidth]{figure_3.png}
  \label{fig:3}
\end{figure}

@@

We thanks to Geert van den Bogaart for his wisdom.

@@

RJCB and FB conceived the idea for this research. 
RJCB wrote the code.
RJCB and FB wrote the article.
